Hyperparamter Optimization

### 2020-07-20 manuscript/manuscript/simulation_study_results.Rmd
corrctions July 20 2020

---
title: "Simulation studies"
output: github_document
bibliography: asreview.bib
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.ncol = 2, out.width = "50%", fig.align = "center", fig.pos = "H") 
options(tinytex.verbose = TRUE)

@@

## Results
First of all, models showed much higher performance for some datasets than for others. While performance on the PTSD (Figure 2a) and the Software dataset (Figure 2b) was quite high, performance was much lower across models for the Nudging (Figure 1a) and Virus (Figure 2d) datasets.

>>>>

---
title: "Simulation studies"
output: github_document
bibliography: asreview.bib
csl: elsevier-vancouver.csl
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.ncol = 2, out.width = "50%", fig.align = "center", fig.pos = "H") 
options(tinytex.verbose = TRUE)

@@

## Results
The figures below shows the recall curves of simulations for all model-dataset combinations. These curves plot recall as a function of the proportion of publications screened. The curves represent the average recall over 15 trials $\pm$ the standard error of the mean in the direction of the y-axis. The x-axis is cut off at 40% since all for simulations, the models reached 95% recall after screening 40% of the publications. The dashed horizontal lines indicate the RRF@10 values, the dashed vertical lines the WSS@95 values. The dashed grey diagonal line corresponds to the expected recall curve when publications are screened in a random order.

First of all, models showed much higher performance for some datasets than for others. While performance on the PTSD (Figure 2a) and the Software dataset (Figure 2b) was quite high, performance was much lower across models for the Nudging (Figure 1a) and Virus (Figure 2d) datasets.

### 2020-07-20 simulation_study/hpoptimization/README.Rmd
update simulations
corrctions July 20 2020

```{bash, eval = FALSE}
asreview hyper-active -t 12:00:00 -m nb -b double -e tfidf -q max -d ace
```

@@

```{r loss_function}
# loss i where x is index, a.k.a. loss plot sorted from high to low loss.
loss_i <- function(trials){
  trials %>%
  ggplot(aes(x = index, y = loss)) +
  geom_line(aes(group = datasets, colour = group), lineend = "round") + 
  geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) + 
  labs(title = "Loss plot", x = "Trials sorted from high to low loss") +
    theme_minimal()
}

# loss t where x is trials, loss plot is sorted over time
loss_t <- function(trials){
  trials %>%
    ggplot(aes(x = trial, y = loss)) +
    geom_line(aes(group = datasets, colour = group), lineend = "round") + 
    geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) +
    labs(title = "Loss plot", x = "Over trials") +
    theme_minimal()
}
```

@@

>>>>

```{bash, eval = FALSE}
asreview hyper-active -t 12:00:00 -m nb -b double -e tfidf -q max -d ../../datasets/test_datasets/ace
```

@@

```{r loss_function}
# loss i where x is index, a.k.a. loss plot sorted from high to low loss.
loss_i <- function(trials){
  trials %>%
  ggplot(aes(x = index, y = loss)) +
  geom_line(aes(group = datasets, colour = group), lineend = "round") + 
  geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) + 
  labs(title = "Loss plot", x = "Trials sorted from high to low loss") +
    theme_bw() + 
    theme(legend.position = 'none')

}

# loss t where x is trials, loss plot is sorted over time
loss_t <- function(trials){
  trials %>%
    ggplot(aes(x = trial, y = loss)) +
    geom_line(aes(group = datasets, colour = group), lineend = "round") + 
    geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) +
    labs(title = "Loss plot", x = "Over trials") +
    theme_bw() +
    theme(legend.position = 'none')

}
```

@@

```{r}

nbtfidftrials$group <-  relevel(nbtfidftrials$group , "one")

nbtfidftrials %>%
  filter(group == "one") %>%
    ggplot(aes(x = trial, y = loss)) +
    geom_line(aes(group = datasets, colour = datasets), lineend = "round", alpha = 0.8) + 
    geom_dl(aes(label = datasets, size = 2), colour = "black", method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) +
  #geom_label(aes(label = datasets, colour = datasets)) +
  scale_colour_viridis_d() +
    labs(title = "Optimizing hyperparameters through a random search", x = "Over trials") +
  scale_x_continuous(limits = c(0,6000)) +
    theme_bw() +
    theme(legend.position = 'none')

nbtfidftrials %>%
  filter(group == "one") %>%
  ggplot(aes(x = index, y = loss)) +
  geom_line(aes(group = datasets, colour = group), lineend = "round") + 
  geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) + 
 scale_fill_manual(values= c("#CC6666","#66CC99"))+
  labs(title = "Optimizing hyperparameters through a random search", x = "Trials sorted from high to low loss") +
    theme_bw() + 
    theme(legend.position = 'none')

nbtfidftrials %>%
   filter(group != "n") %>%
  ggplot(aes(x = index, y = loss)) +
  geom_line(aes(group = datasets, colour = group), lineend = "round") + 
  geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) + 
 scale_fill_manual(values= c("#CC6666","#66CC99"))+
  labs(title = "Optimizing hyperparameters through a random search", x = "Trials sorted from high to low loss") +
  theme_bw() + 
  theme(legend.position = 'none')

nbtfidftrials %>%
  filter(group == "n-1") %>%
    ggplot(aes(x = trial, y = loss)) +
    geom_line(aes(group = datasets, colour = datasets), lineend = "round", alpha = 0.8) + 
    geom_dl(aes(label = datasets, size = 2), colour = "black", method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) +
  #geom_label(aes(label = datasets, colour = datasets)) +
  scale_colour_viridis_d() +
    labs(title = "Optimizing hyperparameters through a random search", x = "Over trials") +
  scale_x_continuous(limits = c(0,2000)) +
    theme_bw() +
    theme(legend.position = 'none')
